---
title: "exp13_results"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(forcats)
```

```{r}
source("./make_paper_plots.R")
```
# exp13 - smaller scenario space

This Rmd creates plots that are specially formatted for the paper submission.

* To create faceted plots in LaTex, putting legend only inside occmean plot.


## Load results

```{r read_results}
exp13_ldr_metrics <- read.csv("exp13/exp13_ldr_metrics.csv", stringsAsFactors = TRUE)
exp13_pp_metrics <- read.csv("exp13/exp13_pp_metrics.csv", stringsAsFactors = TRUE)
exp13_obs_metrics <- read.csv("exp13/exp13_obs_metrics.csv", stringsAsFactors = TRUE)

# Combine
exp13_metrics <- rbind(exp13_ldr_metrics, exp13_pp_metrics, exp13_obs_metrics)

rm(exp13_ldr_metrics)
rm(exp13_pp_metrics)
rm(exp13_obs_metrics)
```

```{r read_predictions_results}
exp13_ldr_predictions <- read.csv("exp13/exp13_ldr_predictions.csv", stringsAsFactors = TRUE)
exp13_pp_predictions <- read.csv("exp13/exp13_pp_predictions.csv", stringsAsFactors = TRUE)
exp13_obs_predictions <- read.csv("exp13/exp13_obs_predictions.csv", stringsAsFactors = TRUE)

# Combine
exp13_predictions <- rbind(exp13_ldr_predictions, exp13_pp_predictions, exp13_obs_predictions)

rm(exp13_ldr_predictions)
rm(exp13_pp_predictions)
rm(exp13_obs_predictions)
```

## Recode factors

```{r}
exp13_metrics$model <- recode_factor(exp13_metrics$model, 
                                      lassocv="LASSO",
                                      lm="LM",
                                      poly="POLY",
                                      rf="RF",
                                      nn="NNET",
                                      svr="SVR",
                                      load="LOAD",
                                      sqrtload = "SQRTLOAD",
                                      erlangc="ERLANGC",
                                      condmeanwaitldr="MGC")


exp13_metrics$measure_nice <- recode_factor(exp13_metrics$measure, 
                                      occmean="mean occupancy",
                                      occp95="95%ile occupancy",
                                      probblocked="probability blocked",
                                      condmeantimeblocked="conditional mean time blocked")

exp13_metrics$unit_nice <- recode_factor(exp13_metrics$unit, 
                                      obs="Observation",
                                      ldr="LDR",
                                      pp="Postpartum"
                                      )

exp13_metrics$qdata_nice <- recode_factor(exp13_metrics$qdata, 
                                      noq="None (NQ)",
                                      basicq="Basic (BQ)",
                                      q="Advanced (AQ)",
                                      onlyq="Only (OQ)"
                                      )
```

```{r}
table(exp13_metrics$model)
```


```{r}
exp13_predictions$model <- recode_factor(exp13_predictions$model, 
                                      lassocv="LASSO",
                                      lm="LM",
                                      poly="POLY",
                                      rf="RF",
                                      nn="NNET",
                                      svr="SVR",
                                      load="LOAD",
                                      sqrtload = "SQRTLOAD",
                                      erlangc="ERLANGC",
                                      condmeanwaitldr="MGC")


exp13_predictions$measure_nice <- recode_factor(exp13_predictions$measure, 
                                      occmean="mean occupancy",
                                      occp95="95%ile occupancy",
                                      probblocked="probability blocked",
                                      condmeantimeblocked="conditional mean time blocked")

exp13_predictions$unit_nice <- recode_factor(exp13_predictions$unit, 
                                      obs="Observation",
                                      ldr="LDR",
                                      pp="Postpartum"
                                      )

exp13_predictions$qdata_nice <- recode_factor(exp13_predictions$qdata, 
                                      noq="None (NQ)",
                                      basicq="Basic (BQ)",
                                      q="Advanced (AQ)",
                                      onlyq="Only (OQ)"
                                      )
```


## Aggregated performance over folds

To start, let's look at aggregated model performance over the 5 folds of the k-crossfold
validation process. A few notes:

* filtered out the pure queueing approximations for now (i.e. I'm only included fitted models)
* for occupancy statistics and conditional mean wait time we use MAPE
* for probability of blocking we use MAE (more relevant and easier to interpret)

### Overall aggregation

```{r aggregation}
(exp13_metrics_agg <- exp13_metrics %>% 
  group_by(unit, unit_nice, measure, measure_nice, qdata, model) %>% 
  summarize(
    train_mape = mean(train_mean_absolute_percentage_error),
    test_mape = mean(test_mean_absolute_percentage_error),
    train_mae = mean(train_mean_absolute_error),
    test_mae = mean(test_mean_absolute_error)
    
  ))
```




## Plots of performance on test data


### LDR

```{r ldr_plots}
which_unit <- 'ldr'
which_subtitle <- ''

plot_height <- 4
plot_width <- 6

plt_ldr_occmean_mape <- mm_paper_error_plot(exp13_metrics_agg, unit = which_unit,
                                       measure = 'occmean', error = 'mape',
                                       title = 'EXP2: LDR - mean occupancy',
                                       subtitle = which_subtitle)
ggsave(plt_ldr_occmean_mape, filename = 'exp13/paper_summary_plots/exp13_ldr_occmean_mape.png',
       height = plot_height, width = plot_width)

plt_ldr_occp95_mape <- mm_paper_error_plot(exp13_metrics_agg, unit = which_unit,
                                      measure = 'occp95', error = 'mape',
                                      title = 'EXP2: LDR - 95%ile occupancy',
                                      subtitle = which_subtitle)
ggsave(plt_ldr_occp95_mape, filename = 'exp13/paper_summary_plots/exp13_ldr_occp95_mape.png',
       height = plot_height, width = plot_width)

plt_ldr_probblocked_mae <- mm_paper_error_plot(exp13_metrics_agg, unit = which_unit,
                                       measure = 'probblocked', error = 'mae',
                                       title = 'EXP2: LDR - probability blocked',
                                       subtitle = which_subtitle)
ggsave(plt_ldr_probblocked_mae, filename = 'exp13/paper_summary_plots/exp13_ldr_probblocked_mae.png',
       height = plot_height, width = plot_width)

plt_ldr_condmeantimeblocked_mape <- mm_paper_error_plot(exp13_metrics_agg, unit = which_unit,
                                      measure = 'condmeantimeblocked', error = 'mape',
                                      title = 'EXP2: LDR - conditional mean time blocked',
                                      subtitle = which_subtitle)
ggsave(plt_ldr_condmeantimeblocked_mape, filename = 'exp13/paper_summary_plots/exp13_ldr_condmeantimeblocked_mape.png',
       height = plot_height, width = plot_width)
```

## PP

```{r pp_plots}
which_unit <- 'pp'
which_subtitle <- ''

plot_height <- 4
plot_width <- 6

plt_pp_occmean_mape <- mm_paper_error_plot(exp13_metrics_agg, unit = which_unit,
                                       measure = 'occmean', error = 'mape',
                                       title = 'EXP2: PP - mean occupancy',
                                       subtitle = which_subtitle)
ggsave(plt_pp_occmean_mape, filename = 'exp13/paper_summary_plots/exp13_pp_occmean_mape.png',
       height = plot_height, width = plot_width)

plt_pp_occp95_mape <- mm_paper_error_plot(exp13_metrics_agg, unit = which_unit,
                                      measure = 'occp95', error = 'mape',
                                      title = 'EXP2: PP - 95%ile occupancy',
                                      subtitle = which_subtitle)
ggsave(plt_pp_occp95_mape, filename = 'exp13/paper_summary_plots/exp13_pp_occp95_mape.png',
       height = plot_height, width = plot_width)


```

## OBS

```{r ldr_plots}
which_unit <- 'obs'
which_subtitle <- ''

plot_height <- 4
plot_width <- 6

plt_obs_occmean_mape <- mm_paper_error_plot(exp13_metrics_agg, unit = which_unit,
                                       measure = 'occmean', error = 'mape',
                                       title = 'EXP2: OBS - mean occupancy',
                                       subtitle = which_subtitle)
ggsave(plt_obs_occmean_mape, filename = 'exp13/paper_summary_plots/exp13_obs_occmean_mape.png',
       height = plot_height, width = plot_width)

obs_occ95_note <- 'Note: Poly model with advanced queueing terms produces non-sensical results due to overfitting.'
plt_obs_occp95_mape <- mm_paper_error_plot(exp13_metrics_agg, unit = which_unit,
                                      measure = 'occp95', error = 'mape',
                                      title = 'EXP2: OBS - 95%ile occupancy',
                                      subtitle = which_subtitle, note = NULL,
                                     ylim_ub = 0.15)
ggsave(plt_obs_occp95_mape, filename = 'exp13/paper_summary_plots/exp13_obs_occp95_mape.png',
       height = plot_height, width = plot_width)

plt_obs_probblocked_mae <- mm_paper_error_plot(exp13_metrics_agg, unit = which_unit,
                                       measure = 'probblocked', error = 'mae',
                                       title = 'EXP2: OBS - probability blocked',
                                       subtitle = which_subtitle)
ggsave(plt_obs_probblocked_mae, filename = 'exp13/paper_summary_plots/exp13_obs_probblocked_mae.png',
       height = plot_height, width = plot_width)

plt_obs_condmeantimeblocked_mape <- mm_paper_error_plot(exp13_metrics_agg, unit = which_unit,
                                      measure = 'condmeantimeblocked', error = 'mape',
                                      title = 'EXP2: OBS - conditional mean time blocked',
                                      subtitle = which_subtitle)
ggsave(plt_obs_condmeantimeblocked_mape, filename = 'exp13/paper_summary_plots/exp13_obs_condmeantimeblocked_mape.png',
       height = plot_height, width = plot_width)
```

## Predicted vs Actual plots

### LDR

```{r ldr_occmean_pred_vs_act}
plt_ldr_occmean_pvsa <- exp13_predictions %>% 
  filter(unit == 'ldr',
         qdata != 'onlyq', 
         model %in% c('LASSO', 'POLY', 'NNET', 'RF'),
         measure == 'occmean') %>% 
  ggplot() +
  geom_point(aes(x=actual, y=prediction), 
             size=1) + geom_abline(intercept = 0, slope = 1) +
  facet_grid(model~qdata_nice) +
  labs(
    title = "EXP2: LDR - mean occupancy predictions vs actual",
    subtitle = "Queueing features by model type",
    caption = NULL,
    tag = NULL,
    x = "Actual value",
    y = "Predicted value",
    colour = "Feature set",
  ) + 
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

plt_ldr_occmean_pvsa
ggsave('exp13/paper_pvsa_plots/exp13_ldr_occmean_pvsa.png')
```

```{r ldr_probblocked_pred_vs_act}
plt_ldr_probblocked_pvsa <- exp13_predictions %>% 
  filter(unit == 'ldr',
         qdata != 'onlyq', 
         model %in% c('LASSO', 'POLY', 'NNET', 'RF'),
         measure == 'probblocked') %>% 
  ggplot() +
  geom_point(aes(x=actual, y=prediction), 
             size=1) + geom_abline(intercept = 0, slope = 1) +
  facet_grid(model~qdata_nice) +
  labs(
    title = "EXP2: LDR - probability blocked predictions vs actual",
    subtitle = "Queueing features by model type",
    caption = NULL,
    tag = NULL,
    x = "Actual value",
    y = "Predicted value",
    colour = "Feature set",
  ) + 
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

plt_ldr_probblocked_pvsa
ggsave('exp13/paper_pvsa_plots/exp13_ldr_probblocked_pvsa.png')
```

```{r ldr_condmeantimeblocked_pred_vs_act}
plt_ldr_condmeantimeblocked_pvsa <- exp13_predictions %>% 
  filter(unit == 'ldr',
         qdata != 'onlyq', 
         model %in% c('LASSO', 'POLY', 'NNET', 'RF'),
         measure == 'condmeantimeblocked') %>% 
  ggplot() +
  geom_point(aes(x=actual, y=prediction), 
             size=1) + geom_abline(intercept = 0, slope = 1) +
  facet_grid(model~qdata_nice) +
  labs(
    title = "EXP2: LDR - conditional mean time blocked predictions vs actual",
    subtitle = "Queueing features by model type",
    caption = NULL,
    tag = NULL,
    x = "Actual value",
    y = "Predicted value",
    colour = "Feature set",
  ) + 
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

plt_ldr_condmeantimeblocked_pvsa
ggsave('exp13/paper_pvsa_plots/exp13_ldr_condmeantimeblocked_pvsa.png')
```
#### Only Q 

```{r}
exp13_predictions %>% 
  filter(unit == 'ldr',
         qdata == 'onlyq', 
         model %in% c('LM')) %>%
  group_by(measure) %>% 
  summarize(
    num_scenarios = n()
  )
```

```{r}
condtime_debug <- exp13_predictions %>% 
  filter(unit == 'ldr',
         qdata == 'onlyq', 
         measure == 'condmeantimeblocked',
         model %in% c('LM'))
```

```{r}
exp13_metrics %>% 
  filter(unit == 'ldr',
         qdata == 'onlyq', 
         model %in% c('LM')) %>%
  group_by(measure) %>% 
  summarize(
    num_scenarios = n()
  )
```

```{r ldr_onlyq_pred_vs_act}
exp13_ldr_onlyq_pvsa <- exp13_predictions %>% 
  filter(unit == 'ldr',
         qdata == 'onlyq', 
         model %in% c('LM')) %>% 
  ggplot() +
  geom_point(aes(x=actual, y=prediction), 
             size=1) + geom_abline(intercept = 0, slope = 1) +
  facet_wrap(~measure_nice, scales = 'free') +
  labs(
    title = "EXP2: LDR - linear model with only queueing approximation terms",
    subtitle = "Predicted vs Actual",
    caption = NULL,
    tag = NULL,
    x = "Actual value",
    y = "Predicted value",
    colour = "Feature set",
  ) + 
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

exp13_ldr_onlyq_pvsa
ggsave('exp13/paper_pvsa_plots/exp13_ldr_onlyq_pvsa.png')
```
```{r ldr_lm_q_pred_vs_act}
exp13_ldr_lasso_q_pvsa <- exp13_predictions %>% 
  filter(unit == 'ldr',
         qdata %in% c('q'), 
         model %in% c('LASSO')) %>% 
  ggplot() +
  geom_point(aes(x=actual, y=prediction), 
             size=1) + geom_abline(intercept = 0, slope = 1) +
  facet_wrap(~measure_nice, scales = 'free') +
  labs(
    title = "EXP2: LDR - LASSO model",
    subtitle = "Predicted vs Actual",
    caption = NULL,
    tag = NULL,
    x = "Actual value",
    y = "Predicted value",
    colour = "Feature set",
  ) + 
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

exp13_ldr_lasso_q_pvsa
ggsave('exp13/paper_pvsa_plots/exp13_ldr_lasso_q_pvsa.png')
```

### OBS
```{r obs_probblocked_pred_vs_act}
plt_obs_probblocked_pvsa <- exp13_predictions %>% 
  filter(unit == 'obs',
         qdata != 'onlyq', 
         model %in% c('LASSO', 'POLY', 'NNET', 'RF'),
         measure == 'probblocked') %>% 
  ggplot() +
  geom_point(aes(x=actual, y=prediction), 
             size=1) + geom_abline(intercept = 0, slope = 1) +
  facet_grid(model~qdata_nice) +
  labs(
    title = "EXP2: OBS - probability blocked",
    subtitle = "Predicted vs Actual",
    caption = NULL,
    tag = NULL,
    x = "Actual value",
    y = "Predicted value",
    colour = "Feature set",
  ) + 
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

plt_obs_probblocked_pvsa
ggsave('plt_obs_probblocked_pvsa.png')
```
```{r ldr_occp95_pred_vs_act}
plt_ldr_occp95_pvsa <- exp13_predictions %>% 
  filter(unit == 'ldr',
         qdata != 'onlyq', 
         model %in% c('LASSO', 'POLY', 'NNET', 'RF'),
         measure == 'occp95') %>% 
  ggplot() +
  geom_point(aes(x=actual, y=prediction), 
             size=4) + geom_abline(intercept = 0, slope = 1) +
  facet_grid(model~qdata_nice) +
  labs(
    title = "EXP2: LDR - 95%ile occupancy predictions vs actual",
    subtitle = "Queueing features by model type",
    caption = NULL,
    tag = NULL,
    x = "Actual value",
    y = "Predicted value",
    colour = "Feature set",
  ) + 
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

plt_ldr_occp95_pvsa
ggsave('exp13/paper_pvsa_plots/exp13_ldr_occp95_pvsa.png')
```

```{r pp_occp95_pred_vs_act}
plt_pp_occp95_pvsa <- exp13_predictions %>% 
  filter(unit == 'pp',
         qdata != 'onlyq', 
         model %in% c('LASSO', 'POLY', 'NNET', 'RF'),
         measure == 'occp95') %>% 
  ggplot() +
  geom_point(aes(x=actual, y=prediction), 
             size=4) + geom_abline(intercept = 0, slope = 1) +
  facet_grid(model~qdata_nice) +
  labs(
    title = "EXP2: PP - 95%ile occupancy",
    subtitle = "Predicted vs Actual",
    caption = NULL,
    tag = NULL,
    x = "Actual value",
    y = "Predicted value",
    colour = "Feature set",
  ) + 
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

plt_pp_occp95_pvsa
ggsave('exp13/paper_pvsa_plots/exp13_pp_occp95_pvsa.png')
```